---
title: "lec1"
author: "JR"
date: "15/09/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

## What is included?
- `readr::read_*` function to load a given rectangular, plain text data set into R
- `<-` assignment symbol to assign values to objects in R
- `readr::write_csv()` to write a df to a .csv file
- `select`
- `filter`
- `mutate`
- `arrange`
- `desc`
- `slice`
- `pull`
- `%in%`
- `%>%` pipe operator to combine 2+ functions
- What is "tidy data"? and what are pros and cons of the tidy data format?
- How do you use `tidyr::pivot_wider` and `tidyr::pivot_longer` in R?



```{r}
library(tidyverse)
can_lang1 <- read_csv("../ds_block1/523_r_prog/private_notes/data/can_lang.csv")
head(can_lang1)
```
### How do you skip rows when reading in data? `read_csv(data="", skip=n)`

```{r}
can_lang2 <- read_csv("../ds_block1/523_r_prog/private_notes/data/can_lang-meta-data.csv", skip = 2, )
head(can_lang2)
```
- to skip rows at the bottom, use `n_max=` argument.
- to see the max line: in **terminal**: `wc -l FILEPATH`, `tail -n 10 FILEPATH`: print the last 10 lines of the file


```{r}

```

